BIOL424 Project Proposal

### 2021-08-21 proposal.tex
Load hyperref in the proposal document, to ensure papers are linked to.
The project specifications require links to cited papers.
Including DOIs in the bibliography and loading hyperref should fulfil this.
Add the relevant literature section to the project proposal.

@@

>>>>

\usepackage{hyperref}

@@

In no particular order:
\begin{itemize}
	\item
		\Textcite{allesina2009food} addressed the optimal grouping of species in order to reduce the number of parameters in a model.
		However, they deal with food webs, rather than competitive interactions, and with binary links, rather than quantitative interactions.
	\item
		\Textcite{maynard2020predicting} provide a method of predicting the outcomes of community dynamics given the results of smaller set of experiments than would traditionally be required.
		However, they do not parameterise a model in doing so, and can predict only the equilibrium points of assemblages.
	\item
		\Textcite{uriarte2004spatially} is one of a number of studies that have attempted to group species using groups selected \emph{a priori} based upon functional or phylogenetic factors.
		In particular, the authors of this paper consider and compare both functional and phylogenetic groupings.
		However, they still only consider four groupings, selected \emph{a priori}, out of more than a googol possible groupings.
	\item
		\Textcite{ovaskainen2017species} fitted models of community dynamics that were not parameterised directly by interaction coefficients, but by the responses of species to ``community-level drivers'': weighted averages of the abundances of various species in the community.
		This is a similar technique to grouping (and in fact includes grouping as a subcase where weights are restricted to zero and one), but requires \emph{a priori} definition of the number of community-level drivers.
		Further, its interpretation may be rather distinct from grouping, depending upon results.
	\item
		\Textcite{weiss2021disentangling} address the problem of too many parameters by making the assumption that many of the interaction coefficients are zero.
		Precisely which coefficients are zero is selected on the basis of model fit, rather than \emph{a priori}.
		However, this still assumes that many pairs of species do not interact: an assumption that need not be made by a model based on grouping.
\end{itemize}
